Incentivizing Exploration with Unbiased History

### 2018-11-02 intro-intro.tex
intro to intro

\ascomment{Nicole, it is all yours ..}

>>>>

In the classic literature on multi-armed bandits, an agent repeatedly selects one of a set of actions, each of which has a payoff drawn from an unknown fixed distribution.  Over time, she can trade off {\em exploitation}, in which she picks an action to maximize her expected reward, with {\em exploration}, in which she takes potentially sub-optimal actions to learn more about their rewards.  By coordinating her actions across time, she can guarantee an average reward which converges to that of the optimal action in hindsight at a rate proportional to the inverse square-root of the time horizon.

In many decision problems of interest, the actions are not chosen by a single agent, as above, but rather a sequence of agents.  In such settings, each agent will choose an exploitive action as the benefits of explorative actions are only accrued by future agents.  For example, in online retail, products are purchased by a sequence of customers, each of which buys what she estimates to be the best available product.  This behavior can cause herding, in which all agents eventually take a sub-optimal action of maximum expected payoff given the available information.

This situation can be circumvented by a centralized algorithm that induces agents to take explorative actions, a line of work called {\em incentivizing exploration}.  One way to induce exploration is to introduce payments~\cite{}.  For example, an online retailer can give coupons to agents for trying certain products.  When payments are financially or technologically infeasible, another alternative is to rely on {\em information asymmetry}~\cite{Kremer-JPE14}.  Here the idea is that the centralized algorithm can choose to selectively release information about the past actions and rewards to the agents in the form of a {\em message}.  Importantly, agents can not directly observe the past, but only learn about it through this message.  The agent then chooses an action, using the content of the message as input.  These systems are often referred to as {\em recommendation systems} as the content of the message can be interpreted as a recommendation for a particular action.

\ascomment{Nicole, it is all yours ..} \nicomment{So now I propose skipping from here to the ``Our scope'' part.  BTW I'd be in favor of deleting those headers (except for the related work one).  Just breaks the flow imo.}
